---
title: "Professional Report Title"
subtitle: "Report Subtitle"
author: "Shubham Dutta, Ph.D."
date: today
date-format: "MMMM D, YYYY"
format:
  pdf:
    template: template_report.tex
    header-text: "Shubham Dutta" # change top left header
    pdf-engine: xelatex
    fig-cap-location: bottom
    tbl-cap-location: top
execute:
  echo: true
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(knitr)
library(shubhamPalette)
library(kableExtra)

knitr::opts_chunk$set(echo = TRUE,
                      dev = "ragg_png",
                      dpi = 400)

theme_set(shubhamPalette::theme_shubhamd(base_family = "Roboto"))
#theme_set(theme_void())
```

# Introduction

This template demonstrates the use of brand colors and custom typography in a professional report. The design system includes:

-   **Typography**
    -   Headings: Roboto Slab
    -   Body Text: Roboto
    -   Code: JetBrains Mono
-   **Colors**
    -   Primary: Deep Navy (`#2D3047`)
    -   Secondary: Forest Green (`#419D78`)
    -   Accents: Golden Yellow (`#E0A458`) and Coral (`#E76F51`)

## Colors

```{r}
#| label: colors
display_shubhamd_colors()
```

## Sample Visualization

```{r}
#| label: fig-example
#| fig-cap: "Example visualization using brand colors"
#| fig-width: 5
#| fig-height: 4

ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  scale_color_shubhamd() +
  labs(
    title = "Vehicle Weight vs Fuel Efficiency",
    subtitle = "Grouped by Number of Cylinders",
    x = "Weight (1000 lbs)",
    y = "Miles per Gallon",
    color = "Cylinders"
  )
```

## Sample Table

```{r}
#| label: tbl-example
#| tbl-cap: "Example table using brand colors"

mtcars %>%
  head() %>%
  kbl() %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    latex_options = c("striped"),
    full_width = FALSE
  ) %>%
  row_spec(0, bold = TRUE)
```

# Methods

## Code Example

Here's an example of how code blocks look in this template:

```{r}
summary_stats <- mtcars %>%
  group_by(cyl) %>%
  summarise(
    mean_mpg = mean(mpg),
    sd_mpg = sd(mpg),
    n = n()
  )

print(summary_stats)
```

# Results

## Mathematical Equations

The template also supports mathematical equations:

$$
f(x) = \int_{-\infty}^{\infty} \hat{f}(\xi)\,e^{2 \pi i \xi x} \,d\xi
$$

# Discussion

This section demonstrates how different heading levels look in the document.

## Subsection Example

This shows a subsection with the secondary brand color.

### Sub-subsection Example

This shows the lowest heading level.

# References {.unnumbered}
