---
title: "Professional Report Title"
subtitle: "Report Subtitle"
author:
  - name: "Shubham Dutta, Ph.D."
    email: contact@shubhamdutta.com
    affiliations:
      - name: UMass Chan Medical School
date: today
format:
  typst:
    template: template_report_dev.typ
fig-format: png
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(knitr)
library(sdtools)
library(kableExtra)
library(gt)

knitr::opts_chunk$set(echo = TRUE,
                      dev = "ragg_png",
                      dpi = 400)

theme_set(sdtools::theme_sd(base_family = "Roboto", major_tick_length = -1))
```

# Introduction

This template demonstrates the use of brand colors and custom typography in a professional report. The design system includes:

-   **Typography**
    -   Headings: Roboto Slab
    -   Body Text: Roboto
    -   Code: JetBrains Mono
-   **Colors**
    -   Primary: Deep Navy (`#2D3047`)
    -   Secondary: Forest Green (`#419D78`)
    -   Accents: Golden Yellow (`#E0A458`) and Coral (`#E76F51`)

## Colors

```{r}
#| label: colors
display_colors_d("main")
```

## Sample Visualization

```{r}
#| label: fig-example
#| fig-cap: "Example visualization using brand colors"
#| fig-width: 5
#| fig-height: 4
#| echo: false

ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  scale_color_shubham_d() +
  scale_x_continuous(expand = expansion(0)) +
  scale_y_continuous(expand = expansion(0)) +
  guides(x.sec = "axis", y.sec = "axis") +
  labs(
    title = "Vehicle Weight vs Fuel Efficiency",
    subtitle = "Grouped by Number of Cylinders",
    x = "Weight (1000 lbs)",
    y = "Miles per Gallon",
    color = "Cylinders"
  )
```

```{r}
ggplot(mtcars, aes(x = factor(cyl), y = mpg, fill = factor(cyl))) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_shubham_d() +
  scale_y_continuous(expand = expansion(0)) +
  guides(x.sec = "axis", y.sec = "axis") +
  theme(legend.position = "none") +
  labs(
    title = "MPG Distribution by Cylinder Count",
    subtitle = "Box plots showing fuel efficiency patterns",
    x = "Number of Cylinders",
    y = "Miles per Gallon"
  )
```

```{r}
cyl_summary <- mtcars %>% 
  group_by(cyl) %>% 
  summarise(
    mean_hp = mean(hp),
    se_hp = sd(hp)/sqrt(n())
  )

ggplot(cyl_summary, aes(x = factor(cyl), y = mean_hp, fill = factor(cyl))) +
  geom_bar(stat = "identity", alpha = 0.7) +
  geom_errorbar(aes(ymin = mean_hp - se_hp, ymax = mean_hp + se_hp),
                width = 0.2) +
  scale_fill_shubham_d() +
  scale_y_continuous(expand = expansion(0)) +
  guides(x.sec = "axis", y.sec = "axis") +
  theme(legend.position = "none") +
  labs(
    title = "Average Horsepower by Cylinder Count",
    subtitle = "With standard error bars",
    x = "Number of Cylinders",
    y = "Horsepower"
  )
```

## Sample Table

```{r}
#| label: tbl-example
#| tbl-cap: "Example table using brand colors"
#| tbl-cap-location: bottom
#| eval: true
#| echo: false

mtcars |>
  head() |>
  knitr::kable()
```

# Methods

## Code Example

Here's an example of how code blocks look in this template:

```{r}
temps <- data.frame(
  year = c(1920:1924),
  Jan = c(40.6, 44.2, 37.5, 41.8, 39.3), 
  Jun = c(58.5, 58.7, 57.8, 52.7, 57.7)
)
```

# Results

## Mathematical Equations

The template also supports mathematical equations:

$$
f(x) = \int_{-\infty}^{\infty} \hat{f}(\xi)\,e^{2 \pi i \xi x} \,d\xi
$$

# Discussion

This section demonstrates how different heading levels look in the document.

## Subsection Example

This shows a subsection with the secondary brand color.

### Sub-subsection Example

This shows the lowest heading level.

::: {#refs}
:::