---
title: "Your Presentation Title"
subtitle: "Optional Subtitle"
author: "Your Name"
date: last-modified
---

## Your First Slide {.center}

This is your first slide with some text in Roboto font.

- Bullet point 1
- Bullet point 2
- Bullet point 3

## Code Example {.smaller}

Here's how your R code will look:

```{r}
#| echo: true
library(ggplot2)
library(shubhamPalette)

ggplot(mtcars, aes(wt, mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  scale_color_manual(values = brand_palette("main")) +
  theme_sd() +
  labs(title = "MPG vs Weight by Cylinders",
       x = "Weight (1000 lbs)",
       y = "Miles per Gallon")
```

## Columns Layout {.smaller}

::: {.columns}
::: {.column width="50%"}
### Left Column

- Point 1
- Point 2
- Point 3
:::

::: {.column width="50%"}
### Right Column

```{r}
#| echo: false
plot(pressure)
```
:::
:::

## Special Formatting

> This is a blockquote that will use your brand styling

::: {.alert}
This is an alert box that uses your coral color
:::

## Tables and Lists

| Column 1 | Column 2 | Column 3 |
|----------|----------|----------|
| Value 1  | Value 2  | Value 3  |
| Value 4  | Value 5  | Value 6  |

1. Numbered list item 1
2. Numbered list item 2
   - Nested bullet point
   - Another nested point
3. Numbered list item 3

## Incremental Slides {.smaller}

::: {.incremental}
- First point appears
- Second point will appear
- Third point will appear last
:::

## End Slide {.center}

### Thank You!

[Your Contact Information]{.footer}
